\chapter{Conclusion}\label{chap:conclusion}

We presented a brand new platform for metamorphic distributed robots -- the RoFI
platform. The RoFI platform consists of autonomous modules which can form a
firm mechanical connection between the modules and therefore, create larger,
more sophisticated structures -- RoFI systems.

As the foundational element of the platform, we designed a docking system,
called the RoFI dock, which provides a way to autonomously connect two modules,
form a firm mechanical connection, establish communication lines and share power
between the modules. We showed that the RoFI dock can be manufactured by
commonly available means and that it provides a reasonably reliable and robust
connection. Also, we designed the dock such that it is a self-contained device
which can be easily integrated into various modules.

On top of the docking system, we defined what a module of the platform is. We
built a formalism to describe the modules and also the whole RoFI systems
consisting of multiple modules. Together with this formalism, we also
established the terminology concerning the systems and their reconfiguration, so
the algorithms for reconfiguration can rely on it.

We proposed and demonstrated a novel approach to communication between the
modules by adapting standard TCP/IP networking with a custom physical layer. The
usage of TCP/IP allows for seamless integration with other networks and possibly
the Internet, leverages robustness of well-tested protocols and also allows for
easy adaptation of the state of the art network research.

As an application of the overall platform definition, we designed and built the
\emph{universal module}, which should serve as a simple building block of RoFI
systems. To support the universal module, we designed \emph{RoFI Driver} -- a
collection of libraries and protocols covering the basic functionality of the
modules. The library includes implementation of the dock driver, the network
interface or the remote firmware update through the dock native communication
channel. We also proposed a library to simplify writing of the massively
asynchronous firmware for microcontrollers.

\section{Future Work}

The RoFI platform is an ambitious project with goals beyond the scope of this
thesis. In this thesis, we took a bottom-up approach -- we started with the
design of the modules and gradually worked up to higher levels of abstraction.
In the near future, we would like to continue in the bottom-up approach and turn
the RoFI dock into a self-contained device ready to embed in modules (this boils
down mainly to adding a control circuitry); next, we would like to equip the
universal module with control circuitry and accumulators.

Having the hardware setup described above opens the possibility to take the
up-down approach and focus on the algorithmic aspects of the metamorphic modular
robots -- mainly the control and the reconfiguration. We would like to implement
some already published algorithms and validate them using the hardware setup
provided by the RoFI platform. Then we would like to explore the possibility of
controlling the RoFI systems in a distributed manner as the nature of the
modules seems suitable for the distributed control and could leverage the
computational potential of all robots in the system.

From the long term perspective it could be also interesting to explore topics
related to security (how to prevent inter-module communication sniffing and
manipulation), specification (how to encode abstract task like ``bring me a
ball'' into a formalism suitable for machine processing) or control synthesis
(how to find the sequence of actions to fulfill a given task).

With more applications of the platform, we would like to revisit the design
choices we made and iteratively improve the platform. This might concern e.g.,
the arrangement of the universal module, the physical layer for the
communication or the choice of the microcontroller.